Supplementary Materials

### 2018-05-14 Writeup/sup_mat.tex
sup mat fixation processing.

\usepackage{graphicx}
\usepackage{subfig}
\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
\usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[L]{\textit{}}
 \fancyhead[L]{\textit{Clarke et al (20xx)}}
\renewcommand{\headrulewidth}{0.8pt}
\renewcommand{\footrulewidth}{0.8pt}
\setlength\headheight{14pt}
\fancyfoot[RO] {\thepage}
\usepackage{authblk}
%%%%%%%%%%%%

@@

\begin{table*}
\centering
\small
\begin{tabular}{cc|c}
 		&				& Number of participants\\
 		\hline
Split-half & Adaptive Choice & \\
Split-half & Foraging & \\
Adaptive Choice & Adaptive Choice & \\

\end{tabular}

\caption{Number of participants available for each comparison}
\label{tab:num_per_paradigm}
\end{table*}

>>>>

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
\usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[L]{\textit{}}
 \fancyhead[L]{\textit{Clarke et al (20xx)}}
\renewcommand{\headrulewidth}{0.8pt}
\renewcommand{\footrulewidth}{0.8pt}
\setlength\headheight{14pt}
\fancyfoot[RO] {\thepage}
\usepackage{authblk}
%%%%%%%%%%%%

@@

\begin{table*}
\centering
\small
\begin{tabular}{cc|c}
 			&					& Number of participants\\
\hline
Split-half 	& Adaptive Choice 	& \\
Split-half 	& Foraging 			& \\
Adaptive Choice & Foraging 		& \\
\end{tabular}
\caption{Number of participants available for each comparison}
\label{tab:num_per_paradigm}
\end{table*}

\section{Data processing}

179 trials with invalid key responses were removed. After removing data from the five outlier participants (see above), all remaining incorrect trials ($n=2529$) were removed, leaving a total of 16187 trials over 59 participants.

\subsubsection{Reaction Times}
As expected, reaction times were highly skewed (Figure \ref{fig:splithalf_rt_dists_all}), so were $\log_2$ transformed (in ms units) before the participant means were calculated for each session and target condition (Figure )

\begin{figure}
\centering
\subfigure[]{\includegraphics[width=14cm]{../Scripts/lineseg/scratch/rt_dists.pdf}}
\subfigure[]{\includegraphics[width=14cm]{../Scripts/lineseg/scratch/rt_dists_mean.pdf}}
\caption{Distribution of reaction times in split-half paradigm.}
\label{fig:splithalf_rt_dists_all}
\end{figure}

\subsubsection{Eye movements}

340,138 fixations were recorded. Of these, 7701 fell outside of the stimuli area and were removed. Fixations landing within a vertical strip consisting of $10\%$ of the stimuli's width were classed as \textit{central}. All remaining fixations were then classed as landing on the \textit{homogeneous} or \textit{heterogeneous} half of the stimulus. Initial fixations were not included in the analysis. Numbers of fixations are given in Table \ref{tab:num_fix}.

\begin{table*}
\centering
\small
\begin{tabular}{c|c|r|r|r}
 		&	& $1<n$	& $2 \leq n \leq 5$ & $2 \leq n \leq 3$\\
\hline
\multirow{3}{*}{easy} 
& central		& 3931 	& 3689	& \\
& homogeneous 	& 12452	& 8312 	&\\
& heterogeneous & 5955	& 3241 	&\\
\hline
\multirow{3}{*}{hard} 
& central		& 3804 	& 2439	& \\
& homogeneous 	& 8781	& 3188	&	\\
& heterogeneous & 29912	& 5294	&\\
\hline
\multirow{3}{*}{absent} 
& central		& 16885 & 8303	& \\
& homogeneous 	& 41356	& 12576	&\\
& heterogeneous & 192348& 5763	&\\
\hline
\end{tabular}
\caption{Number of fixations recorded for each condition.}
\label{tab:num_fix}
\end{table*}
